Enhancing Adversarial Robustness for Deep Metric Learning

### 2021-11-04 robdml.tex
tex

\textbf{Adversarial Attack.}
%
Szegedy \etal~\cite{l-bfgs} find misclassification of DNN can be triggered by
an imperceptible adversarial perturbation to the input image.
%
Ian \etal~\cite{fgsm} attribute the reason to DNN being locally linear with
respect to the adversarial perturbation.
%
Subsequent first-order gradient-based methods can compromise the DNNs more
effectively under the white-box assumption~\cite{i-fgsm,madry,apgd}.
%
In contrast, black-box attacks have been explored by query-based
methods~\cite{nes-atk,spsa-atk} and transferrability-based methods~[], which
are more practical for real-world scenarios.

@@

\textbf{Attacks in DML.}
%
DML has been found vulnerable to adversarial attacks as
well~\cite{advrank,advorder,robrank}, which raises concerns on safety,
security, or fairness for a DML application.
%
The existing attacks aims to completely subvert the image retrieval
results~[][][], or covertly alter the top-ranking results without being
abnormal~[][][][].

>>>>

\textbf{Adversarial Attack.}
%
Szegedy \etal~\cite{l-bfgs} find misclassification of DNN can be triggered by
an imperceptible adversarial perturbation to the input image.
%
Ian \etal~\cite{fgsm} attribute the reason to DNN being locally linear with
respect to the adversarial perturbation.
%
Subsequent first-order gradient-based methods can compromise the DNNs more
effectively under the white-box assumption~\cite{i-fgsm,madry,apgd}.
%
In contrast, black-box attacks have been explored by query-based
methods~\cite{nes-atk,spsa-atk} and transferrability-based
methods~\cite{di-fgsm}, which are more practical for real-world scenarios.

@@

\textbf{Attacks in DML.}
%
DML has been found vulnerable to adversarial attacks as
well~\cite{advrank,advorder,robrank}, which raises concerns on safety,
security, or fairness for a DML application.
%
The existing attacks aims to completely subvert the image retrieval
results~\cite{qair,learn-to-misrank,advdpqn,advpattern,flowertower,universalret},
or covertly alter the top-ranking results without being
abnormal~\cite{advrank,advorder}.
